---
title: "Medical Expense Data Analysis and Predictive Modeling"
output:
  github_document:
       pandoc_args: --webtex

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
library(feather)
library(tidyverse)
library(knitr)
library(caret)
library(ggridges)
library(ggthemes)
theme_set(theme_minimal())
set.seed(123)
```

# Summary of the data set

```{r load data}
# code template  
```


- summary of the data  
- prject proposal
- research quetions


# Exploratory analysis on the training data set 

To understand the nature of predictors with respect to `Medical Expenses` we will perform Exploratory Data Analysis and we will try to understand if there are some intresting behaviours.

##### 1. Let's see how `Medical Expenses` are changing with `Age`

<html>
<img src = '../../reports/figures/1.Expenses_VS_Age.png'>
</html>

It can be observed that `Medical Expense` of people is increasing, as `Age` increases.

##### 2. Let's see how  `Medical Expenses` are changing with `BMI (Body Mass Index)`

<html>
<img src = '../../reports/figures/2.Expenses_VS_BMI.png'>
</html>

The highest expenses seem to occur for people who have a higher BMI.

##### 3. Let's see how much money males and females spending on medical treatments between 18-64 Years

<html>
<img src = '../../reports/figures/3.Expenses_VS_Gender.png'>
</html>

The expenses seem to grow with age for both males and females. It looks like Males in their **20's & 60's** tend to pay more on their `Medical Expenses` than Females. Females in their **40's** are paying more than Males on their `Medical Expenses`.


##### 4. Let's see how `Smokers` and `Non-Smokers` are spending on medical treatments between 18-64 Years

We expect expenditures by smokers should be higher than the non smokers.

<html>
<img src = '../../reports/figures/4.Expenses_VS_Smoker.png'>
</html>

**Interesting!!!** - As expected, Health expenses of smokers are a lot higher than the one of non-smokers.

##### 5. Let's see how `BMI` is changing with Age for Males and Females

We are expecting both male and females have usual `BMI`.

<html>
<img src = '../../reports/figures/5.BMI_VS_AGE.png'>
</html>

The `BMI` doesn't seem to vary depending on the age nor the sex.

##### 6. Let's see the Male & Female Expenses Over BMI

<html>
<img src = '../../reports/figures/6.EXP_VS_BMI.png'>
</html>

The highest expenses seem to occur for people from both genders who have a BMI that is higher than 34.

# Answering the Inferential Research Questions 

Now, from above Exploratory Data Analysis we are interested in following two questions:

  - Is there a significant difference of expenses between smokers and non-smokers? 
  - Is there a significant difference of expenses between males and females?

<br> 

##### 1. Is there a significant difference of expenses between smokers and non-smokers? 

$$H_0: \mu_{Smokers} = \mu_{Non-Smokers}$$
$$H_1: \mu_{Smokers} \neq \mu_{Non-Smokers}$$

Our Null hypothesis states that mean expenses of smokers is equal to mean expenses of non-smokers and Alternate hypothesis states that there is a significant difference between these two quantities. We have used t-test to compare mean of two groups and test results are as following:

```{r}
hypothesis_1 <- readr::read_csv('../../reports/tables/1.hypothesis_smokers.csv')
kableExtra::kable(hypothesis_1)
```

The exact p-value is $`r hypothesis_1$p.value`$ which is very close to 0. However, while rendering the output to the table above it treats it as 0.

As, we can observe that the p-values is less than the significance level of $5\%$ hence, we can reject $H_0$ hypothesis and conclude that we have enough evidence to say mean expenses between smoker and no-smokers is not same. 

##### 2. Is there a significant difference of expenses between males and females?

$$H_0: \mu_{Males} = \mu_{Females}$$
$$H_1: \mu_{Males} \neq \mu_{Females}$$

Our Null hypothesis states that mean expenses of males is equal to mean expenses of females and Alternate hypothesis states that there is a significant difference between these two quantities. We have used t-test to compare mean of two groups and test results are as following:

```{r}
hypothesis_2 <- readr::read_csv('../../reports/tables/2.hypothesis_sex.csv')
kableExtra::kable(hypothesis_2)
```

The exact p-value is $`r hypothesis_2$p.value`$ which is less than the significance level of $5\%$ hence, we can reject $H_0$ hypothesis and conclude that we have enough evidence to say mean expenses between Males and Females is not same. 

# Build a predictive model 
- description
- model selection
- hyper-parameter tuning

# Evaluate the predictive model 
- model evaluation on train and test
- results
- regression plots

# References 



